The evolution of gene expression in the term placenta of viviparous mammals

### 2016-01-28 manuscript/manuscript.Rnw
add top genes table

    }
    return(invisible(temp.table[order(`p (t-test)`),]))
}
@

>>>>

    }
    return(invisible(temp.table[order(`p (t-test)`),]))
}
output.top.genes.table <- function(data,output=TRUE) {
    if (output) {
        table.display <- c("s","s","s","d")
        table.align <- c("c","c","p{3in}","r")
        if (any(colnames(data) %in% "FPKM SEM"))  {
            table.display <- c(table.display,"d")
            table.align <- c(table.align,"r")
        }
        if (any(colnames(data) %in% "Human Symbol"))  {
            table.align <- c("c",table.align)
            table.display <- c("s",table.display)
        }
        print(xtable(data,
                     display=table.display,
                     align=table.align
                     ),
              booktabs=TRUE,
              floating=FALSE,
              sanitize.text.function=genes.table.sanitize,
              include.rownames=FALSE)
    }
}
